---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RcLoggers

<!-- badges: start -->
<!-- badges: end -->

The goal of RcLoggers is to get a complex function and requires too much memory to run via Shiny onto your computer so you can run it yourself.

## Installation

You can install the development version of RcLoggers from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("add-am/RcLoggers")
```

## Using The Function

Currently only one function is provided: `logger_extract()`. A basic example of using this function is as follows:

```{r}
#| eval: FALSE

#load the library
library(RcLoggers)

#run the function (basic)
data_extract <- logger_extract(
  Years = 2025,
  Loggers = "BUR2"
)

```

This function does have some more advanced options:

```{r}
#| eval: FALSE

#run the function (detailed)
data_extract <- logger_extract(
  Years = c(2024, 2025), #you can dowload more than one year
  Loggers = c("BUR1", "BUR2"), #you can download more than one logger
  FilterFlags = TRUE, #you can filter data by quality flag
  FlagTags = c(1,2), #if you decide to filter you then provide the flag tags to keep
  AggregateToDaily = FALSE #you can aggregate data to get a daily value rather than a 10-minute value
)

```